---
title: "RtaskVithia"
format: html
editor: visual
---

# R resources and tasks

### Links:

A\) http://www.sthda.com/english/wiki/r-basics-quick-and-easy - STHDA is a very useful R site

B\) https://r4ds.hadley.nz/ - Tidyverse is a new way of writing R code that makes it much cleaner and easier to follow. This book is by the people who made Tidyverse. Tidyverse is going to be essential for working with data.

C\) https://epirhandbook.com/en/ggplot-basics.html - ggplot2 is the default R plotting package, and is mostly very good (we can discuss some things that ggplot cannot do, but at a later stage). Definitely try out the exercises in here to familairise yourselves with ggplot2!

## Tasks

### Task 1 - Install latest version of RStudio

At first this was completed by visitng the R studio site. Next we found a package that updates base R, called installr.

### Task 2 - Get started with R via. link A, B and C.

fafa

### Task 3 - PlantGrowth data

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false

library("stringr")
library("Racmacs")
library("usethis")
library("tidyverse")
library("dplyr")

```

```{r}
#| echo: false

#Load data
data("ToothGrowth")

#Learn about dataset
?ToothGrowth
```

The dataset compares the length of odontoblasts (cells responsible for toothgrowth) in 60 guinea pigs. Each aminal recieved one of three dose levels of vitamin C, by one of two delivery methods, orange juice (OJ) and asorbic acid (VJ) - a form of vitamin C.

Magnus

```{r}
tooth_data <- ToothGrowth |>
  rename(length = len,
         delivery = supp) 
# use class(tooth_data) to check if it's a dataframe



```

Oliver

```{r}
#| echo: false

#Lets show that when you increase the dose of vitamin C, the length of the tooth changes
ggplot(data = ToothGrowth,
       mapping = aes(x = dose,
                     y = len)) +
  geom_point(aes(color = supp))

#Showing the density of the different lengths compared to delivery methods
ggplot(data = ToothGrowth,
       mapping = aes(x = len)) +
  geom_density(aes(color = supp))

#Boxplot of the two diferent delivery methods. There is no statistical sigificant difference between the two
ggplot(data = ToothGrowth,
       mapping = aes(x = supp, 
                     y = len)) +
  geom_boxplot()

#Boxplot of the different dose levels. This plot does not make much sense tbh
ggplot(data = ToothGrowth,
       mapping = aes(x = dose,
                     y = len)) +
  geom_boxplot(aes(color = supp))
```
