---
title: "RtaskVithia"
format: html
editor: visual
---

# R resources and tasks

### Links:

A\) http://www.sthda.com/english/wiki/r-basics-quick-and-easy - STHDA is a very useful R site

B\) https://r4ds.hadley.nz/ - Tidyverse is a new way of writing R code that makes it much cleaner and easier to follow. This book is by the people who made Tidyverse. Tidyverse is going to be essential for working with data.

C\) https://epirhandbook.com/en/ggplot-basics.html - ggplot2 is the default R plotting package, and is mostly very good (we can discuss some things that ggplot cannot do, but at a later stage). Definitely try out the exercises in here to familairise yourselves with ggplot2!

## Tasks

### Task 1 - Install latest version of RStudio

At first this was completed by visitng the R studio site. Next we found a package that updates base R, called installr.

### Task 2 - Get started with R via. link A, B and C.

fafa

### Task 3 - PlantGrowth data

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false

library("Racmacs")
library("usethis")
library("tidyverse")
```

```{r}
#| echo: false

#Load data
data("PlantGrowth")  

#View data
View(PlantGrowth)

#Learn about dataset
?PlantGrowth
```

The dataset compares the yield obtained under a control and two different treatment conditions, which created a dataframe (df) of 30 cases on 2 variables.

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
